### 2019-02-18 manuscript/introduction.tex

%B: I placed this out of order, so you can see it
The prevalence and significance of polyploidy was broadly considered a salient feature of flowering plants \citep{}, even before the advent of genomic tools dramatically escalated the stakes, so that nearly flowering plants are thought to have undergone at least one round of polyploidization \citep{}.
It is therefore perhaps surprising that there appears to be little agreement regarding the evolutionary consequences of polyploidy, especially how it affects diversification rates. %species richness.
% I think Rosana wants this part here (above)
% next, continue with ploidy narrative (mayrose/soltis)

>>>>

%B: I placed this out of order, so you can see it
The prevalence and significance of polyploidy was broadly considered a salient feature of flowering plants \citep{}, even before the advent of genomic tools dramatically escalated the stakes, so that nearly flowering plants are thought to have undergone at least one round of polyploidization \citep{}.
It is therefore surprising that there is little agreement regarding the evolutionary consequences of polyploidy, especially how it affects diversification rates. %species richness.
% I think Rosana wants this part here (above)
% next, continue with ploidy narrative (mayrose/soltis)

### 2019-02-18 manuscript/methods.tex

To those existing data sets, we added some additional records for chromosome number and breeding system.
The Supplementary Information contains citations for the numerous sources for the added data. % todo: add number of refs when we have it
Resolution of taxonomic synonymy followed the conventions provided in Solanaceae Source \citep{solsource}. 
Hybrids and cultivars were excluded because ploidy and breeding system can be affected by artificial selection during domestication.
Following the reasoning outlined in \citet{robertson_2011}, we examined closely the few species for which the merged ploidy and breeding system data indicated the presence of self-incompatible polyploids.
Although SI populations frequently contain some SC individuals, and diploid populations frequently contain some polyploid individuals, in no case did we find a convincing case of a naturally occurring SI and polyploid population.
%B: Thus qualified, as above, I think this should be inserted.
The single instance of an SI and polyploid individual appears to be an allopentaploid hybrid of {\em Solanum oplocense} Hawkes x {\em Solanum gourlayii} Hawkes, reported by \citet{camadro_1981}.
Under exceedingly rare circumstances, it is possible for polyploids containing multiple copies of S-loci to remain SI, so long as they express a single allele at the S-locus (discussed in \citealt{robertson_2011}).
Because of the resulting absence of SI and polyploid populations, as well as the linked functional explanation for disabling of gametophytic self-incompatibility systems with non-self recognition, following whole genome duplication \citep[reviewed in][]{ramsey_1998,stone_2002}, we consider only three observed character states: self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids which are always self-compatible (CP).
%B: I added the non-self recognition bit, because in Prunus, heteroallelic pollen may not cause SC.
% E: Should we include more details about how many polymorphic species and how the particularly tricky ones were dealt with? %B: No and yes, maybe. Interested parties can go to data for part 1?

@@

@@

@@

>>>>

To those existing data sets, we added some additional records for chromosome number and breeding system.
The Supplementary Information contains citations for the numerous sources for the added data. % todo: add number of refs when we have it
Resolution of taxonomic synonymy followed the conventions provided in Solanaceae Source \citep{solsource}. 
Hybrids and cultivars were excluded because ploidy and breeding system can be affected by artificial selection during domestication.
Following the reasoning outlined in \citet{robertson_2011}, we examined closely the few species for which the merged ploidy and breeding system data indicated the presence of self-incompatible polyploids.
Although SI populations frequently contain some SC individuals, and diploid populations frequently contain some polyploid individuals, in no case did we find a convincing case of a naturally occurring SI and polyploid population.
%B: Thus qualified, as above, I think this should be inserted.
The single instance of an SI and polyploid individual appears to be an allopentaploid hybrid of {\em Solanum oplocense} Hawkes x {\em Solanum gourlayii} Hawkes, reported by \citealt{camadro_1981}.
Under exceedingly rare circumstances, it is possible for polyploids containing multiple copies of S-loci to remain SI, so long as they express a single allele at the S-locus (discussed in \citealt{robertson_2011}).
Because of the resulting absence of SI and polyploid populations, as well as the linked functional explanation for disabling of gametophytic self-incompatibility systems with non-self recognition, following whole genome duplication \citep[reviewed in][]{ramsey_1998,stone_2002}, we consider only three observed character states: self-incompatible diploids (ID), self-compatible diploids (CD), and polyploids which are always self-compatible (CP).
%B: I added the non-self recognition bit, because in Prunus, heteroallelic pollen may not cause SC.
% E: Should we include more details about how many polymorphic species and how the particularly tricky ones were dealt with? %B: No and yes, maybe. Interested parties can go to data for part 1?

@@

% B (via E): need some explanation of what \delta means, biologically, when ploidy is scored like this

@@

% E todo: explain "pathway" method of robertson2011

@@

% E: Could we include a figure of the traits on the tree?  At least as supp info. TODO
